Regular singular Volterra equations on complex domains

### 2023-08-09 reg-sing-volterra.tex
Add comments to sec:example

Let $\Omega_{a}$ be a simply connected open set $\Omega_a\subset\C$ that touches but doesn't contain $\zeta=a$ and let $\Gamma_a^\theta$ be the ray that leaves $a$ at angle $\theta$. If $\Gamma_a^\theta$ is contained in $\Omega_a$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\Omega_a)$ with $\sigma>-1$ and $\lambda>0$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$ ~\cite[Section 5.6]{diverg-resurg-i}. It is defined by the formula

@@

\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, a}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, a} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{a}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
where $p$ is any point on the position domain $\Omega$.

@@

Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ and
\[ \laplace_{\zeta,a}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_{\zeta,a}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,a}^\theta \varphi.
\end{equation}
for all integers $n \ge 0$ and suitable direction $\theta$.

@@

    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}

>>>>

Let $\Omega_{a}$ be a simply connected open set $\Omega_a\subset\C$ that touches but doesn't contain $\zeta=a$ and let $\Gamma_a^\theta$ be the ray that leaves $a$ at angle $\theta$. If $\Gamma_a^\theta$ is contained in $\Omega_a$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\Omega_a)$ with $\sigma>-1$ and $\textcolor{magenta}{\Lambda}>0$ \textcolor{magenta}{[I don't think we need $\Lambda > 0$. For $\Lambda \le 0$, the Laplace transform should still produce functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$, which in this case will include $z = 0$]} to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$~\cite[Section 5.6]{diverg-resurg-i} \textcolor{magenta}{[I think we want $\Re(z e^{-i\theta}) > \Lambda$]}. It is defined by the formula

@@

\subsubsection{Action on integral operators}\label{L-int-op}
%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, a}$ is defined by \textcolor{orange}{[are we changing the definition of $\partial^{\nu-1}_{\zeta, a}$ so that $a$ is a point, rather than a $\zeta$ value?]}
\[ [\partial^{\nu-1}_{\zeta, a} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{a}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
where $p$ is any point on the position domain $\Omega$ \textcolor{orange}{[let's use a different letter here, since $p$ is already used; maybe $b$ for the base point and $a$ for the evaluation point, to match our discussion of $f_0$]}.

@@

Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$? can we do this with Proposition~\ref{prop:smoothing}?]} and
\[ \laplace_{\zeta,a}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$. This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_{\zeta,a}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,a}^\theta \varphi.
\end{equation}
for all integers $n \ge 0$ and suitable direction $\theta$.

@@

    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ \textcolor{magenta}{[to get this from our uniqueness result, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]} and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}
